The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-06 manuscript/manuscript.Rnw
rearrange results sections to discuss results under their major type

\subsection{\dog Placenta Transcriptome}

\subsection{\cow Placenta Transcriptome}

\subsection{\elephant Placenta Transcriptome}

\subsection{\armadillo Placenta Transcriptome}

\subsection{Opossum Placenta Transcriptome}

\subsection{Mouse Placenta Transcriptome}

@@

\subsection{\textit{Nannospalax galili} (Blind Mole Rat) Placenta Transcriptome}

@@

\subsection{\textit{Spalax carmeli} (Blind Mole Rat) Placenta Transcriptome}

@@

\subsection{Wild Boar Placenta Transcriptome}

\begin{table}[h]
  \tiny
<<top.50.pig.expressed.genes,echo=FALSE,results="asis">>=
top.pig.genes <- top.genes.table(species.name="sus scrofa")
print(xtable(top.pig.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.pig.genes,"Gene symbol")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not ribosomal, 
mitochondrial, or whose human ortholog is a housekeeping gene in
  \textit{Sus scrofa}}
\label{tab:top50_pig_placenta}
\end{table}

@@

\subsection{\horse Placenta Transcriptome}

@@

\subsection{\sheep Placenta Transcriptome}

@@

@@

\subsection{\ac{GSE} Analyses of Individual Transcriptomes}

>>>>

\subsection{Rodentia}

\subsubsection{Mouse Placenta Transcriptome}

@@

\subsubsection{\textit{Nannospalax galili} (Blind Mole Rat) Placenta Transcriptome}

@@

\subsubsection{\textit{Spalax carmeli} (Blind Mole Rat) Placenta Transcriptome}

@@

\subsection{Laurasiatheria}

\subsubsection{\dog Placenta Transcriptome}

\subsubsection{\cow Placenta Transcriptome}

\subsubsection{\pig Placenta Transcriptome}

\begin{table}[h]
  \tiny
<<top.50.pig.expressed.genes,echo=FALSE,results="asis">>=
top.pig.genes <- top.genes.table(species.name="sus scrofa")
print(xtable(top.pig.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.pig.genes,"Gene symbol")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not ribosomal, 
mitochondrial, or whose human ortholog is a housekeeping gene in
  \pig}
\label{tab:top50_pig_placenta}
\end{table}

@@

\subsubsection{\horse Placenta Transcriptome}

@@

\subsubsection{\sheep Placenta Transcriptome}

@@

\subsection{Atlantogenata}
\subsubsection{\elephant Placenta Transcriptome}

\subsubsection{\armadillo Placenta Transcriptome}

\subsection{Metatherians}

\subsubsection{\opossum Placenta Transcriptome}

@@

\subsubsection{\ac{GSE} Analyses of Individual Transcriptomes}
